A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-08-06 ionic_liquids.tex

In Table \ref{table:henry} we present the results of solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}.
Table~\ref{table:henry} also contains the experimental $K_s$ reported by Mahurin \textit{et al.} \cite{Mahurin_2010} and Finotello \textit{et al.} \cite{Finotello_2008}.
The uncertainties in $K_s$ were calculated using standard error propagation.

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at T = 298.15 K and P = 1 atm.
The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
\begin{tabular}{ c c c  c  c  c  c }  
\toprule
Model & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
			\hline
			\multicolumn{4}{c}{\ce{[emim][B(CN)_4]}} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
			\hline
Koller \textit{et al.} \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
Batista \textit{et al.} \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
Liu \textit{et al.} \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
Weber y Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
\hline
		\multicolumn{4}{c}{[emim][Tf\textsubscript{2}N]} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
		\hline
 K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
 \bottomrule
\label{table:henry} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

@@

The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf\textsubscript{2}]}. 
The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm this result.
The SDFs of the ions around a \ce{CO_2} molecule were obtained by using the software packages TRAVIS \cite{Brehm_2011} and VMD \cite{HUMP96}.
For that, we carried out NPT-MD simulations of \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] systems with a \ce{CO_2} molar fraction of 0.1.
The isovalues were visually determined so as to observe the first solvation shell.
If we compare Figs.~\ref{fig:sdf_ions} (a) and (b), one notes that the region with a low probability of finding an ion is larger for \ce{[emim][NTf_2]}.
Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.
\begin{figure}[ht]
\centering
\subfloat[]{%
  \includegraphics[width=\linewidth]{kollerall.pdf}%
}

@@

Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].
The differences in the \ce{CO_2} molar fractions in this case exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, mentioned at the introduction of this paper.

\begin{table*}
\centering
\begin{threeparttable}
\caption{Thermodynamic conditions employed in the simulations of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]~\cite{Makino_2014,Schilderman_2007}}
\begin{tabular}{ c  c  c  c  c  }  
\toprule
Ionic liquid & T (K)  & P (atm)  & molar fraction $x_s$ & molality $m_s$ \\
\midrule		
$\text{[emim]}$[B(CN)\textsubscript{4}]~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
$\text{[emim]}$[Tf\textsubscript{2}N]~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
 \bottomrule
\label{table:solv} 
\end{tabular}
\end{threeparttable}
\end{table*}

In Fig.~\ref{fig:pressure} we show for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably lower for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
In addition, we see that for  this system the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] were -0.755 $\pm$ 0.01 kcal/mol and -0.542 $\pm$ 0.005, respectively. However, since we employed a different molecule number of \ce{CO_2}, we cannot draw any conclusion regarding the presence of strong interactions with \ce{[emim][B(CN)_4]} that could explain the higher solubility.

\begin{figure}[ht]
\includegraphics[width=\linewidth]{pressure_est.pdf}
\caption{ \ce{CO_2} \ce{[emim][B(CN)_4]} Koller \textit{et al.} \cite{Koller_2012}, (squares)}
\label{fig:pressure}
\end{figure}

@@

The task of accurately predicting $\gamma^{\, \infty}$ is challenging since, according to Eq.~\eqref{eq:gamma_inf}, one should reproduce the solvation free energies in both the pure solute and the solvent.
In Table~\ref{table:mu_solutes} we show the simulated densities and the solvation free energies $(\Delta G^{0}_{\text{sim}})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}.
It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ for cyclohexane.
Note that only in the case of ethanol we successfully predicted the $\Delta G^{0}_\text{exp}$.
The relative errors for the other solutes is around 10\%.

@@

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Solvation free energy at $T = 298.15~/text{K}$ for the pure solutes benzene, hexane, cyclohexane, ethanol and water.}
\begin{tabular}{ c c c c c c c c }
\toprule
Solute & $\rho_{\text{sim}}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
 & (g/cm$^{3}$) &  & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   &  \\
\hline
benzene OPLS-AA   & 0.8611 $\pm$ 0.0002 & 1.4 & -3.75  $\pm$ 0.02 & -0.381 $\pm$ 0.007 & -4.14 $\pm$ 0.02 & -4.56 & 9.32  \\
hexane OPLS-AA    & 0.6513 $\pm$ 0.0003 & 0.5 & -3.67  $\pm$  0.03 & 0.011 $\pm$ 0 & -3.66 $\pm$ 0.03 & -4.06 & 9.90 \\
cyclohexane & 0.7692 $\pm$ 0.0007 & 0.6 & -4.39 $\pm$ 0.01 & 0 & -4.39 $\pm$ 0.01 & - & -  \\
ethanol TRAPPE-UA   & 0.781 $\pm$ 0.008 & 1.01  &-0.93 $\pm$ 0.01 & -4.15 $\pm$ 0.02  & -5.08  $\pm$ 0.02  & -5.08 & 0 \\
water TIP4P/2005   &  0.9948 $\pm$ 0.0003 & 0.2 & 2.015 $\pm$ 0.004 & -9.01 $\pm$ 0.02 & -6.99 $\pm$ 0.02 & -6.33  &10.43 \\
 \bottomrule
\label{table:mu_solutes} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(Z^{\text{exp}} - Z^{\text{sim}})/Z^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]} at $T = 298.15~/text{K}$ of the pure solutes benzene, hexane, cyclohexane, ethanol, and water.}
\begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
\toprule
Solute & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
 & (kcal/mol) & (kcal/mol) &  (kcal/mol)  &  & (298.15 K) \cite{Doma_ska_2011} & (303 K) \cite{Yan_2010} \\
\midrule % inserts single-line
hexane OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
cyclohexane& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
benzene OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
ethanol TRAPPE-UA& -0.73 $\pm$ 0.02 & -4.10 $\pm$ 0.04 & -4.83 $\pm$ 0.04 & 0.41 $\pm$ 0.03 & 1.58 & 1.64  \\
water TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
 \bottomrule
\label{table:gamma} 
\end{tabular}
\end{threeparttable}
\end{adjustbox}
\end{table*}
\section{Concluding remarks}
\label{sec:conclusion}

>>>>

In Table \ref{table:henry} we present the results of the solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}.
Table~\ref{table:henry} also contains the experimental $K_s$ reported by Mahurin \textit{et al.} \cite{Mahurin_2010} and Finotello \textit{et al.} \cite{Finotello_2008}.
The uncertainties in $K_s$ were calculated using standard error propagation.

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at $T$ = $298.15~\text{K}$ and $P$ = $1~\text{atm}$.
The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
\begin{tabular}{ c c c  c  c  c  c }  
\toprule
Model & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
			\hline
			\multicolumn{4}{c}{\ce{[emim][B(CN)_4]}} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
			\hline
Koller \textit{et al.} \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
Batista \textit{et al.} \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
Liu \textit{et al.} \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
Weber y Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
\hline
		\multicolumn{4}{c}{[emim][Tf\textsubscript{2}N]} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
		\hline
 K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
 \bottomrule
\label{table:henry} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

@@

The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf\textsubscript{2}]}. 
The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm this result.
The SDFs of the ions around a \ce{CO_2} molecule were obtained by using the software packages TRAVIS \cite{Brehm_2011} and VMD \cite{HUMP96}.
For that, we carried out NPT-MD simulations of \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] systems with a \ce{CO_2} molar fraction of 0.1.
The isovalues were visually determined so as to observe the first solvation shell.
If we compare Figs.~\ref{fig:sdf_ions} (a) and (b), one notes that the region with a low probability of finding an ion is larger for \ce{[emim][NTf_2]}.
Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.~\ref{fig:sdf_ions} (c).
\begin{figure}[ht]
\centering
\subfloat[]{%
  \includegraphics[width=\linewidth]{kollerall.pdf}%
}

@@

Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table~\ref{table:solv}, which correspond to similar values of \ce{CO_2} molality.
Note that the differences in the \ce{CO_2} molar fractions clearly exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, which was mentioned at the introduction of this paper.

\begin{table*}
\centering
\begin{threeparttable}
\caption{Thermodynamic conditions employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}~\cite{Makino_2014,Schilderman_2007}.}
\begin{tabular}{ c  c  c  c  c  }  
\toprule
Ionic liquid & T (K)  & P (atm)  & molar fraction $x_s$ & molality $m_s$ \\
\midrule		
$\text{[emim]}$[B(CN)\textsubscript{4}]~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
$\text{[emim]}$[Tf\textsubscript{2}N]~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
 \bottomrule
\label{table:solv} 
\end{tabular}
\end{threeparttable}
\end{table*}

For each system, in Fig.~\ref{fig:pressure} we show our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably lower for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
In addition, we see that in this case the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} were -0.755 $\pm$ 0.01 kcal/mol and -0.542 $\pm$ 0.005, respectively.
However, since we simulated a different molecule number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could be a factor contributing to the higher solubility.

\begin{figure}[ht]
\includegraphics[width=\linewidth]{pressure_est.pdf}
\caption{Prediction of the gas-phase fugacity and partial pressure of \ce{CO_2} for the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}.}
\label{fig:pressure}
\end{figure}

@@

The task of accurately predicting $\gamma^{\, \infty}$ is challenging since, according to Eq.~\eqref{eq:gamma_inf}, one should reproduce the solvation free energies in both the pure solute and the solvent.
In Table~\ref{table:mu_solutes} we show the simulated densities and the solvation free energies $(\Delta G^{0}_{\text{sim}})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}.
It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ for cyclohexane.
Note that only in the case of ethanol we successfully predicted the $\Delta G^{0}_\text{exp}$.
The relative errors for the other solutes are around 10\%.

@@

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Solvation free energy at $T = 298.15~\text{K}$ for the pure solutes benzene, hexane, cyclohexane, ethanol and water.}
\begin{tabular}{ c c c c c c c c }
\toprule
Solute & $\rho_{\text{sim}}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
 & (g/cm$^{3}$) &  & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   &  \\
\hline
benzene OPLS-AA   & 0.8611 $\pm$ 0.0002 & 1.4 & -3.75  $\pm$ 0.02 & -0.381 $\pm$ 0.007 & -4.14 $\pm$ 0.02 & -4.56 & 9.32  \\
hexane OPLS-AA    & 0.6513 $\pm$ 0.0003 & 0.5 & -3.67  $\pm$  0.03 & 0.011 $\pm$ 0 & -3.66 $\pm$ 0.03 & -4.06 & 9.90 \\
cyclohexane & 0.7692 $\pm$ 0.0007 & 0.6 & -4.39 $\pm$ 0.01 & 0 & -4.39 $\pm$ 0.01 & - & -  \\
ethanol TRAPPE-UA   & 0.781 $\pm$ 0.008 & 1.01  &-0.93 $\pm$ 0.01 & -4.15 $\pm$ 0.02  & -5.08  $\pm$ 0.02  & -5.08 & 0 \\
water TIP4P/2005   &  0.9948 $\pm$ 0.0003 & 0.2 & 2.015 $\pm$ 0.004 & -9.01 $\pm$ 0.02 & -6.99 $\pm$ 0.02 & -6.33  &10.43 \\
 \bottomrule
\label{table:mu_solutes} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(Z^{\text{exp}} - Z^{\text{sim}})/Z^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]} at $T = 298.15~\text{K}$ of the pure solutes benzene, hexane, cyclohexane, ethanol, and water.}
\begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
\toprule
Solute & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
 & (kcal/mol) & (kcal/mol) &  (kcal/mol)  &  & (298.15 K) \cite{Doma_ska_2011} & (303 K) \cite{Yan_2010} \\
\midrule % inserts single-line
hexane OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
cyclohexane& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
benzene OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
ethanol TRAPPE-UA& -0.73 $\pm$ 0.02 & -4.10 $\pm$ 0.04 & -4.83 $\pm$ 0.04 & 0.41 $\pm$ 0.03 & 1.58 & 1.64  \\
water TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
 \bottomrule
\label{table:gamma} 
\end{tabular}
\end{threeparttable}
\end{adjustbox}
\end{table*}
\section{Concluding remarks}
\label{sec:conclusion}
